`r params$project_title`

### 2021-03-16 reports/rmarkdown/02_individual_reports.Rmd
Small buggs

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  #pdf_document:
    #toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  dataset: 1
---

>>>>

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  dataset: 1
---

### 2021-03-16 reports/rmarkdown/03_integrated_datasets.Rmd
Small buggs

```{r, echo = FALSE}
groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
  x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
names(groupings) <- names(datasets_all_samples)[-1]
all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))

>>>>

```{r, eval=FALSE, include=FALSE}
groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
  x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
names(groupings) <- names(datasets_all_samples)[-1]
all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))
